### 2017-07-05 readme.Rmd
fixed minor get_area bug.

For a laugh, let's generate some quasirandom background points and plot them against the presence points. Here we are using the `quasirandom_covariates` method which tries to select quasirandom points across geographic and environmental space. The other working methods are `quasirandom` which just creates quasirandom points spatially, or `grid` which creates a regular grid at a set resolution - this is every similar to the grid design proposed by Warton *et al.,* 2010.
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
sp_sites <- POdata@coords
colnames(sp_sites) <- c("x","y")
bkpts_quasi <- generate_background_points(number_of_background_points = 1000,
                                    known_sites = sp_sites,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'quasirandom')
```

@@

Now let's try and generate a ppm using a Poisson gam. We are going to need more integration points (background points) in order to develop a robust Poisson Point Process model. If you look at the great Fithian & Hastie (2014) or Warton & Shepard (2010) papers they show that if you start to approach an infinite number of integration points you should converge on the correct estimate of the intensity of occurrence (not quite correct) within the study region. Infinity is a big number - so how about we aim for about 20,000 background points. If are getting close the summed relative likelihood of occurrence should approximately equal the number of presence points, in this case study 94 occurrence points.

@@

Now let's plot these models.
```{r,fig.width=8,fig.height=6}
jet.colors <- colorRampPalette(rev(RColorBrewer::brewer.pal(11 , "Spectral")))
plot(p_cell,col=jet.colors(100))
```

@@

Fithian, William, and Trevor Hastie. "Finite-sample equivalence in statistical models for presence-only data." The annals of applied statistics 7.4 (2013): 1917.

@@

Phillips, S. J. and Elith, J. (2013). On estimating probability of presence from use-availability or presence-background data. Ecology 94 1409-1419.

>>>>

For a laugh, let's generate some quasirandom background points and plot them against the presence points. Here we are using the `quasirandom_covariates` method which tries to select quasirandom points across geographic and environmental space. The other working methods are `quasirandom` which just creates quasirandom points spatially, or `grid` which creates a regular grid at a set resolution - this is every similar to the grid design proposed by Warton & Shepard 2010.
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
sp_sites <- POdata@coords
colnames(sp_sites) <- c("x","y")
bkpts_quasi <- generate_background_points(number_of_background_points = 1000,
                                    known_sites = sp_sites,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'quasirandom')
```

@@

Now let's try and generate a ppm using a Poisson gam. We are going to need more integration points (background points) in order to develop a robust Poisson Point Process model. If you look at the great Fithian & Hastie (2015) or Warton & Shepard (2010) papers they show that if you start to approach an infinite number of integration points you should converge on the correct estimate of the intensity of occurrence (not quite correct) within the study region. Infinity is a big number - so how about we aim for about 20,000 background points. If are getting close the summed relative likelihood of occurrence should approximately equal the number of presence points, in this case study 94 occurrence points.

@@

Now let's plot these models.
```{r,fig.width=8,fig.height=6}
jet.colors <- colorRampPalette(rev(RColorBrewer::brewer.pal(11 , "Spectral")))
plot(p_cell,col=jet.colors(100))
points(sp_sites,cex=.5,pch=16)
```

@@

@@
